\toolnameend: A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-04-26 doc/paper.tex
Full paper work. Fixes #136, fixes #128, fixes #129, fixes #130, fixes #131, fixes 134, fixes #135, fixes #139, fixes #143, fixes #144, fixes #149, fixes #150, fixes #152, fixes #166, fixes #168, fixes #174, fixes #176, fixes #189, fixes #191, fixes #192...and maybe some others.

\usepackage{textcomp} 
\usepackage{svg}

@@

	\begin{figure*}[t] \includegraphics[width = \textwidth]{IFargslabel} \caption{A
			picture of \toolname} \centering \label{fig:fullpic} \end{figure*}

@@

	\section{Related Work} \label{related-work} Given humanity's affinity for
	visual information, visualizations have long been prized for their ability to
	communicate information quickly and efficient \cite{baeza1999modern}; the
	visualization of spreadsheets, therefore, has offered much room for research.
	Several previous tools work within a spreadsheet, seeking to clarify the
	connections between the visible values in cells, the formulae that produce
	them, and the dependencies between cells that inform them. Igarashi and
	colleague's fluid visualizations \cite{igarashi1998fluid}, for example, do this
	by imposing lines, color, and animation over the spreadsheet to visually
	explain these tangled connections. Likewise, Clermont explored ways of grouping
	cells by color and border that were related through similar functions,
	neighbors, or references \cite{clermont2003scalable}, and Hipfl extended this
	work by incorporating the layouts and labels of spreadsheets
	\cite{hipfl2008using}. Other tools focus on creating visualizations external to
	the sheets. Hermans and colleagues address a spreadsheet programmer's
	information by making dataflow diagrams from individual sheets through the
	tools GyroSAT \cite{hermans2011supporting} and Breviz \cite{hermans2011breviz}.
	\toolname is among the latter class, creating standalone visualizations about
	spreadsheets. In contrast to Hermans' work, though, our work focuses on
	representing functions and how they comprise complex formula, rather than
	exploring the data structures of any particular spreadsheet.  \par

	Many other tools inspect the structure of formulae but often from the
	perspective of finding bad design.  Following Fowler's initial description of
	code smells in object-oriented design \cite{fowler2009refactoring}, many
	researchers have applied similar observations to spreadsheets and have
	cataloged classes of problematic formulae \cite{hermans2012detecting}
	\cite{cunha2012towards} \cite{asavametha2012detecting}, often accompanying them
	with detection tools \cite{abreu2014smelling} and investigations
	\cite{jansen2015code}. For example, Hermans, leveraging her work with the
	aforementioned dataflow diagrams, has worked with assessing common
	inter-worksheet smells, such as feature envy and inappropriate intimacy,
	wherein references between worksheets (rather than cells) in a file suggest a
	problem. \cite{hermans2012detectinginter}. Other tools, like Badam's Excel
	refactoring \cite{badame2012refactoring}, are concerned more with understanding
	the formula in the service of changing them. However, these studies define
	standards of poor design and orient their searches around them. Though
	\toolname supports the search for bad design, as we will see, the tool itself
	takes a much more agnostic approach in presentation, offering examples without
	regard for design quality. \par

@@

		\item [1] \textbf{Provide an interactive environment for free exploration.}
		There are a lot of data in some of these collections, and the user should be
		able to pick for themselves which to explore while ignoring the rest.
		Furthermore, this exploration should not be designed around answering one
		specific question but rather be open-ended.

		\item [!1] \textbf{Do not make judgments about good and bad design.} Though
		users may certainly approach the tool with the intention of finding particular
		formulae, \toolname will not prioritize any on metrics of good or bad
		practice. Rather, it will present them agnostically, referring only to
		frequency.

		\item [2] \textbf{Emphasize the quantitative patterns in formula
			construction.} \toolname should address the questions of how often the
		spreadsheet programmers used a certain function and where they used it. In
		this way, it must show precise metrics, such as frequency of use and depth of
		function nesting, of the dataset it conveys.

@@

	Though we kept these guidelines in mind through the development of \toolname,
	we nevertheless reached a number of points in which these principles
	conflicted. For a discussion of these decisions, see section
	\ref{ssec:decisions}.

	\subsection{Walkthrough of the Tool} \label{sec:walkthrough}Before discussing
	the minutiae of tool's development, though, we will give a basic example of how
	to use the tool. For this, we will answer this question: \textit{ What kinds of
		functions do people use to define the condition in an IF function?} Thefull
	visualization that answers this is available in figure \ref{fig:fullpic};
	however, to understand the interaction, we will start from the beginning. \par

	First, a word on the IF function. In Excel, it serves as one of the logical
	functions: given a condition as the first argument that evaluates to either
	true or false, it takes on the value of either the second or third argument,
	respectively. Or, as the documentation writes out, "IF(Something is True, then
	do something, otherwise do something
	else)"\footnote{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2?ui=en-US\&rs=en-US\&ad=US}. Furthermore, the third argument is optional; if left out, the function will return a default "FALSE" value if necessary. Examples of this function in practice can be seen in \ref{fig:ifexample}.

	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{ifExample}
		\label{fig:ifexample} \caption{Configurations of the IF function} \end{figure}

	When the user first approaches the tree for a given top-level function -- that
	is, a function nested within none other -- only a few nodes are visible, as
	shown in figure \ref{fig:startpic}. \par

	\begin{figure}[h] \centering \includegraphics{start} \label{fig:startpic}
		\caption{How the IF tree looks at the start} \end{figure}

	The visualization so far comprises two types of node: the circle
	\includegraphics{glossary-greenonly}, which represents a discrete function in
	the formula and is size according to its frequency relative to the number of
	times to root function appeared\footnote{The root node, by definition, will
		always be the largest node in a tree.}; and the numbered squares
	\includegraphics{glossary-blue}, which represent the positions of arguments
	within its parent function. From this, we can confirm that, of the times it was
	observed, IF can have at most three arguments passed into it, which corresponds
	with its specifications in the
	API\footnote{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2}. \par

@@

	\begin{figure}[h] \centering \includegraphics[width=.43\textwidth]{IFexpand}
		\label{fig:expandif} \caption{First argument of the IF tree} \end{figure}

@@

		\item  \vspace{.25cm} \includegraphics{glossary-blue} - \textbf{Argument
			nodes} are dark blue squares labeled with a number. The number is the position
		of an argument within the function in the parent node. In \ref{fig:expandif}
		for example, argument node 1 shows every function or value that was seen in
		the first argument.

@@

	\begin{figure}[h] \centering \includegraphics[width =
		.46\textwidth]{comparison} \includegraphics[]{comparison-ss}
		\label{fig:optional} \caption{The contents of each type of tree.} \end{figure}

@@

	Guided by the goals in section A, we faced a number of decision points, a
	sample of which we describe below, before we arrived at the design shown above.
	\begin{itemize}

@@

	\subsection{Bad Smells} \label{badsmells} Fowler's description of code smells
	\cite{fowler2009refactoring} underscored an important point of code quality:
	between elegant, efficient code and bug-crippled spaghetti, there is a spectrum
	of code designs which, by themselves, are not faulty but nevertheless suggest
	vulnerabilities in code design. Since then, researchers have applied these
	concepts to spreadsheet programming, as discussed in section
	\ref{related-work}. While some of the smells lie beyond the scope of the tool,
	such as those characterizing inter-worksheet connections, others have
	structures which create distinctive features within the tree, leading to easy
	detection through our visualization: \par

@@

		\item \textit{Multiple Operations}: A single formula comprises numerous
		functions and operators. \cite{hermans2012detecting}. As a result, the formula
		tends to be prohibitively complex. In the visualization, since each nested and
		combined function creates yet another level of depth within the tree, these
		constructions can result in long, horizontal chains of nodes, as seen in
		figure \ref{"fig:longsum"}.

@@

	\begin{figure*}[h] \centering \includegraphics[width=\textwidth]{longsum}
		\label{"fig:longsum"} \caption{The horizontal length of a tree may indicate
			complex or redundant design.} \end{figure*}

@@

	\begin{figure} \centering \includegraphics[width=.5\textwidth]{lookupexample}
		\label{fig:lookupexample} \caption{Demonstrations of LOOKUP and VLOOKUP}
	\end{figure}

@@

	All of these variations may seem daunting to a beginner, but \toolname can
	help. Because of its design, users can distinguish between forms of the same
	function, as seen in Figure \ref{fig:lookups} where the one can explore both
	the frequency with which the spreadsheet programmers used these different forms
	-- three-argument vector form much more than the array form -- and then
	retrieve examples of every configuration in the dataset. The same goes for the
	V/HLOOKUP functions, as shown partially in Figure \ref{fig:vhlookups}

	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{lookup-2}
		\includegraphics[width=.5\textwidth]{lookup-3} \label{fig:lookups}
		\caption{LOOKUP with two and three arguments.} \end{figure}

	Furthermore, these examples are good as well for exploring how it might bridge
	issues of bad design with education. In a recent study, Hermans, Aivaloglou,
	and Jansen probed the Enron dataset for uses of VLOOKUP and HLOOKUP
	specifically. The issue at hand was the optional fourth argument, which
	requires that rows are sorted lest it return inaccurate results
	\cite{hermans2015detecting}. For someone seeking to increase awareness of this
	problem, it first allows them to answer the question of significance -- "How
	often do spreadsheet programmers use this function, with these particular
	parameters?" Though \toolname does not discernd whether neighboring columns are
	sorted, it can nevertheless guide the educator to several examples in
	production where this problem surfaces. \par

	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{vlookup}
		\includegraphics[width=.5\textwidth]{hlookup} \label{fig:vhlookups}
		\caption{VLOOKUP and HLOOKUP with four arguments.} \end{figure}

	\section{User Study} \label{sec:userstudy} During development, we conducted a
	brief, four-participant user study in order to detect conflicts between our
	design and the goals in section \ref{goals}. We designed the study to be
	exploratory; given trees based in the Enron dataset and at least twenty
	minutes, we asked the participants to adopt the persona of a consultant
	evaluating a company's spreadsheet practice, allowing for questions like which
	functions on which the employees most depended or which sheets or employees
	presented the most anomalous or dangerous designs. Though we instructed them on
	how to use the tool and suggested that they visit one of the most populous
	trees in the set, we put aside any specific tasks or questions and let them
	choose their own paths. Though interpretation of the phrase ``spreadsheet
	practice" can certainly vary from participant to participant, we readily
	accepted this interpretive flexibility since we wanted a range of views and
	backgrounds despite the persona. We clarified, furthermore, that their
	observations could be directed either at the quality of the data conveyed by
	the tool or at the tool's design itself. \par

@@

	\subsection{Use in Smell Tracking} \begin{wrapfigure}{O}{.25\textwidth}
		\centering \includegraphics{SUM} \label{fig:sum} \caption{An abundance of
			parameters in SUM. Encountering this, P4 remarked, "Woah."} \end{wrapfigure}

	The participants were most vocal about their findings when they discovered, by
	purpose or accident, instances of heinous design in the dataset. Many times,
	they noted these examples shortly after opening a new tree, suggesting that the
	distinctive visual signatures as discussed in section \ref{badsmells} was a
	salient force in their exploration. For example, when P3 encountered the
	initial design of the SUM tree, as seen in figure \ref{fig:sum}, they readily
	diagnosed that either a spreadsheet author was "totally incompetent, or [the
	formula was] just some that's weird." Other than these visual cues, value
	errors, prefixed with \#s, also appear in the tree, which P4 said could be
	useful for tracking these problems if marked well.

@@

	However, we found that even though a user can explore all of a function's
	configurations, this does not mean that they will learn exactly what it does.
	P1, examining unfamiliar functions like KURT and PV, could describe precisely
	what types of arguments it accepted and how many. But even after exploring the
	spreadsheets for context, they could not accurately describe what the functions
	produced without consulting the official documentation. Whether through
	reticence of the tool or obscurity of the functions themselves, the exploratory
	environment is not enough to teach users \textit{when} to use a function.
	However, we could address this in future designs, perhaps, by linking directly
	to such documentation from within the tool without violating any design
	concerns in \ref{goals}. \par

@@

	\section{Discussion} We began these studies with the intention of evaluating
	our progress towards the goals in section \ref{goals}. Working from these
	results, we noted many places where the tool aligned well or fell short.

@@

	Other than that, we did avoid designing anything that intentionally evaluated
	formula designs. Nevertheless, \toolname inadvertently emphasizes bad design of
	certain types, such as all of those in section \ref{badsmells} marked by their
	visual signatures. Even so, our participants found the discovery of bad smell
	to be the most interesting aspect about it, to the point where they could
	imagine business scenarios in which micromanagers use it to ensure precise
	design parameters across a department's spreadsheets! To design in that
	direction, however, would mean a reevaluation of this design goal, since
	intentionally guiding users toward known smells may guide them away from new,
	unmarked ones.

@@

	However, the benefits described in the previous sections imply a hidden
	complication: if the tool educates through example but does not explicitly
	distinguish between good design and bad design, how can we be sure that people
	won’t inadvertently learn bad design from it? In the user study, we discussed
	its use in education and smell detection by bringing up the issues surrounding
	the LOOKUP functions; this discussion, though, presupposes a distinguishing eye
	that knew which examples practiced good design and which exhibited the common
	errors. But a beginner might not know the difference. Robillard and Deline, in
	their study, remarked that good API examples should demonstrate best practices,
	but, right now, we have no way to assure this with \toolname. As with the
	problems in achieving unbiased exploration, correcting for this danger may
	entail a reevaluation of design goals.

@@

	\begin{figure} \centering \includegraphics[width=.5\textwidth]{index}
		\label{fig:index} \caption{A difficult question: how often is MATCH used in
			both the second and third arguments?} \end{figure}

	Though our focus was specifically on function combination, there are several
	other elements of a formula's context that we do no currently consider. For
	example, \toolname does not current capture argument combination; in
	\ref{fig:index}, it is impossible to state how often the function MATCH
	occurred in both the second and third arguments or whether they were more often
	paired with references. Furthermore, it is easy to open a tree and see what is
	used inside of a specific function, but finding information on what a function
	is used inside of takes considerably more work -- we see again in
	\ref{fig:index} that MATCH is used inside INDEX, but we cannot know which
	functions have INDEX inside them without searching every other tree. More
	distant concerns might be exploring which functions often occur in adjacent
	cells in the sheet -- whenever INDEX occurs, which functions are seen most
	often in the cells around it?

@@

	\section{Conclusion} This paper presents a tool to support the exploration of
	function combinations throughout a given spreadsheet dataset. By taking a
	agnostic approach to design quality, it attempts to convey the dataset's
	spreadsheet practices as is: the common along with the anomalous, and the
	well-designed along with the odorous. As seen in the user and case studies,
	this allows it to take on several potential roles at once, such as an
	environment for search out bad code smells as well as a repository for examples
	for learning new techniques. \par

>>>>

\usepackage{textcomp} 
%\usepackage{svg}
%\setsvg{inkscape = inkscape -z -D, svgpath = svgs/}

@@

	\begin{figure*}[t] \centering \includegraphics[scale=.6]{IFargslabel} \caption{A
			picture of \toolname displaying the common arguments to the IF function's first 
			parameter} \centering \label{fig:fullpic} \end{figure*}

@@

	\section{Related Work} \label{related-work} Visualizations have long been prized for their ability to
	communicate information quickly and efficient \cite{baeza1999modern}; the
	visualization of spreadsheets, therefore, has offered much room for research.
	Several previous tools work within a spreadsheet, seeking to clarify the
	connections between the visible values in cells, the formulae that produce
	them, and the dependencies between cells that inform them. Igarashi and
	colleague's fluid visualizations \cite{igarashi1998fluid}, for example, do this
	by imposing lines, color, and animation over the spreadsheet to visually
	explain these tangled connections. Likewise, Clermont explored ways of grouping
	cells by color and border that were related through similar functions,
	neighbors, or references \cite{clermont2003scalable}, and Hipfl extended this
	work by incorporating the layouts and labels of spreadsheets
	\cite{hipfl2008using}. Other tools focus on creating visualizations external to
	the sheets. Hermans and colleagues address a spreadsheet programmer's
	information needs by making dataflow diagrams from individual sheets through the
	tools GyroSAT \cite{hermans2011supporting} and Breviz \cite{hermans2011breviz}.
	\toolname is among the latter class, creating standalone visualizations about
	spreadsheets. In contrast to Hermans' work, our work focuses on
	representing functions and how they comprise complex formula, rather than
	exploring the data structures of any particular spreadsheet.  \par

	Many other tools inspect the structure of formulae but often from the
	perspective of finding bad design.  Following Fowler's initial description of
	code smells in object-oriented design \cite{fowler2009refactoring}, many
	researchers have applied similar observations to spreadsheets and have
	cataloged classes of problematic formulae \cite{hermans2012detecting}
	\cite{cunha2012towards} \cite{asavametha2012detecting}, often accompanying them
	with detection tools \cite{abreu2014smelling} and investigations
	\cite{jansen2015code}. For example, Hermans, leveraging her work with the
	aforementioned dataflow diagrams, has worked with assessing common
	inter-worksheet smells, such as feature envy and inappropriate intimacy,
	wherein references between worksheets (rather than cells) in a file suggest a
	problem \cite{hermans2012detectinginter}. Other tools, like Badam's Excel
	refactoring \cite{badame2012refactoring}, are concerned more with understanding
	the formula in service of changing them. However, these studies define
	standards of poor design and orient their searches around them. Though
	\toolname supports the search for bad design, as we will see, the tool itself
	takes a much more agnostic approach in presentation, offering examples without
	regard for design quality. \par

@@

		\item [1] \textbf{Provide an interactive environment for free exploration.}
		There are a lot of data in some of these spreadsheet corpora, and the user should be
		able to pick for themselves which to explore while ignoring the rest.
		Furthermore, this exploration should not be designed around answering one
		specific question but rather be open-ended.

		\item [!1] \textbf{Do not make judgments about good and bad design.} Though
		users may certainly approach the tool with the intention of finding particular
		formulae, \toolname will not prioritize any on metrics of good or bad
		practice.

		\item [2] \textbf{Emphasize the quantitative patterns in formula
			construction.} \toolname should address the questions of how often the
		spreadsheet programmers used a certain function and where they used it. In
		this way, it must show metrics, such as frequency of use and depth of
		function nesting, of the dataset it conveys.

@@

	Though we kept these guidelines in mind through the development of \toolname,
	we nevertheless reached a number of points in which these principles
	conflicted. For a discussion of these decisions, see Section
	\ref{ssec:decisions}.

	\subsection{Walkthrough of the Tool} \label{sec:walkthrough}Before discussing
	the minutiae of tool's development, though, we will give a basic example of how
	to use the tool. For this, we will answer this question: \textit{ What kinds of
		functions do people use to define the condition in an IF function?} The full
	visualization that answers this is available in Figure~\ref{fig:fullpic};
	however, to understand the interaction, we will start from the beginning. \par

	First, a word on the IF function. In Excel, it serves as one of the logical
	functions: given a condition as the first argument that evaluates to either
	true or false, it takes on the value of either the second or third argument,
	respectively. Or, as the documentation writes out, "IF(Something is True, then
	do something, otherwise do something
	else)"\footnote{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2?ui=en-US\&rs=en-US\&ad=US}. 
	Furthermore, the third argument is optional; if left out, the function will return a default "FALSE" value if necessary. Examples of this function in practice can be seen in Figure~\ref{fig:ifexample}.

	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{ifExample}
		\caption{Configurations of the IF function} \label{fig:ifexample} \end{figure}

	When the user first approaches the tree for a given top-level function -- that
	is, a function nested within none other -- only a few nodes are visible, as
	shown in Figure \ref{fig:startpic}. \par

	\begin{figure}[h] \centering \includegraphics[scale=.5]{start} 
		\caption{How the IF tree looks at the start} \label{fig:startpic} \end{figure}

	The visualization so far comprises two types of nodes: the circle
	\includegraphics{glossary-greenonly}, which represents a discrete function in
	the formula and is size according to its frequency relative to the number of
	times to root function appeared\footnote{The root node, by definition, will
		always be the largest node in a tree.}; and the numbered squares
	\includegraphics{glossary-blue}, which represent the positions of arguments
	within its parent function. From this, we can confirm that, of the times it was
	observed, IF can have at most three arguments passed into it, which corresponds
	with its specifications in the
	API\footnote{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2}. \par

@@

	\begin{figure}[h] \centering \includegraphics[scale=.4]{IFexpand}
		 \caption{First argument of the IF tree} \label{fig:expandif} \end{figure}

@@

		\item  \vspace{.25cm} \includegraphics{glossary-blue} - \textbf{Argument
			nodes} are dark blue squares labeled with a number. The number is the position
		of an argument within the function in the parent node. In Figure \ref{fig:expandif}
		for example, argument node 1 shows every function or value that was seen in
		the first argument.

@@

	\begin{figure}[h] \centering \includegraphics[width =
		.46\textwidth]{comparison} \includegraphics[]{comparison-ss}
		\caption{The contents of each type of tree.} \label{fig:optional} \end{figure}

@@

	Guided by the goals in Section \ref{goals}, we faced a number of decision points, a
	sample of which we describe below, before we arrived at the design shown above.
	\begin{itemize}

@@

	\subsection{Bad Smells} \label{badsmells} Fowler's description of code smells
	\cite{fowler2009refactoring} underscored an important point of code quality:
	between elegant, efficient code and bug-crippled spaghetti, there is a spectrum
	of code designs which, by themselves, are not faulty but nevertheless suggest
	vulnerabilities in code design. Since then, researchers have applied these
	concepts to spreadsheet programming, as discussed in Section
	\ref{related-work}. While some of the smells lie beyond the scope of the tool,
	such as those characterizing inter-worksheet connections, others have
	structures which create distinctive features within the tree, leading to easy
	detection through our visualization: \par

@@

		\item \textit{Multiple Operations}: A single formula comprises numerous
		functions and operators \cite{hermans2012detecting}. As a result, the formula
		tends to be prohibitively complex. In the visualization, since each nested and
		combined function creates yet another level of depth within the tree, these
		constructions can result in long, horizontal chains of nodes, as seen in
		Figure \ref{fig:longsum}.

@@

	\begin{figure*}[h] \centering \includegraphics[width=\textwidth]{longsum}
		 \caption{The horizontal length of a tree may indicate
			complex or redundant design.} \label{fig:longsum} \end{figure*}

@@

	\begin{figure} \centering \includegraphics[width=.5\textwidth]{lookupexample}
		 \caption{Demonstrations of LOOKUP and VLOOKUP} \label{fig:lookupexample}
	\end{figure}

@@

	All of these variations may seem daunting to a beginner, but \toolname can
	help. Because of its design, users can distinguish between forms of the same
	function, as seen in Figure \ref{fig:lookups} where the one can explore both
	the frequency with which the spreadsheet programmers used these different forms
	-- three-argument vector form much more than the array form -- and then
	retrieve examples of every configuration in the dataset. The same goes for the
	V/HLOOKUP functions, as shown partially in Figure \ref{fig:vhlookups}.

	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{lookup-2}
		\includegraphics[width=.5\textwidth]{lookup-3}
		\caption{LOOKUP with two and three arguments}  \label{fig:lookups} \end{figure}

	Furthermore, these examples are good as well for exploring how it might bridge
	issues of bad design with education. In a recent study, Hermans, Aivaloglou,
	and Jansen probed the Enron dataset for uses of VLOOKUP and HLOOKUP
	specifically. The issue at hand was the optional fourth argument, which
	requires that rows are sorted lest it return inaccurate results
	\cite{hermans2015detecting}. For someone seeking to increase awareness of this
	problem, it first allows them to answer the question of significance -- "How
	often do spreadsheet programmers use this function, with these particular
	parameters?" Though \toolname does not discern whether neighboring columns are
	sorted, it can nevertheless guide the educator to several examples in
	production where this problem surfaces. \par

	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{vlookup}
		\includegraphics[width=.5\textwidth]{hlookup} 
		\caption{VLOOKUP and HLOOKUP with four arguments} \label{fig:vhlookups}\end{figure}

	\section{User Study} \label{sec:userstudy} During development, we conducted a
	brief, four-participant user study in order to detect conflicts between our
	design and the goals in Section \ref{goals}. We designed the study to be
	exploratory; given trees based in the Enron dataset and at least twenty
	minutes, we asked the participants to adopt the persona of a consultant
	evaluating a company's spreadsheet practice, allowing for questions like which
	functions on which the employees most depended or which sheets or employees
	presented the most anomalous or dangerous designs. Though we instructed them on
	how to use the tool and suggested that they visit one of the most populous
	trees in the set, we put aside any specific tasks or questions and let them
	choose their own paths. Though interpretation of the phrase ``spreadsheet
	practice" can certainly vary from participant to participant, we readily
	accepted this interpretive flexibility since we wanted a range of views and
	backgrounds despite the persona. We clarified, furthermore, that their
	observations could be directed either at the quality of the data conveyed by
	the tool or at the tool's design itself. \par

@@

	\subsection{Use in Smell Tracking} \begin{wrapfigure}{O}{.25\textwidth}
		\centering \includegraphics{SUM}  \caption{An abundance of
			parameters in SUM. Encountering this, P4 remarked, "Woah."} \label{fig:sum} \end{wrapfigure}

	The participants were most vocal about their findings when they discovered, by
	purpose or accident, instances of heinous design in the dataset. Many times,
	they noted these examples shortly after opening a new tree, suggesting that the
	distinctive visual signatures as discussed in Section \ref{badsmells} was a
	salient force in their exploration. For example, when P3 encountered the
	initial design of the SUM tree, as seen in Figure \ref{fig:sum}, they readily
	diagnosed that either a spreadsheet author was "totally incompetent, or [the
	formula was] just some that's weird." Other than these visual cues, value
	errors, prefixed with \#s, also appear in the tree, which P4 said could be
	useful for tracking these problems if marked well.

@@

	However, we found that even though a user can explore all of a function's
	configurations, this does not mean that they will learn exactly what it does.
	P1, examining unfamiliar functions like KURT and PV, could describe precisely
	what types of arguments it accepted and how many. But even after exploring the
	spreadsheets for context, they could not accurately describe what the functions
	produced without consulting the official documentation. Whether through
	reticence of the tool or obscurity of the functions themselves, the exploratory
	environment is not enough to teach users \textit{when} to use a function.
	However, we could address this in future designs, perhaps, by linking directly
	to such documentation from within the tool without violating any design
	concerns in Section \ref{goals}. \par

@@

	\section{Discussion} We began these studies with the intention of evaluating
	our progress towards the goals in Section \ref{goals}. Working from these
	results, we noted many places where the tool aligned well or fell short.

@@

	Other than that, we did avoid designing anything that intentionally evaluated
	formula designs. Nevertheless, \toolname inadvertently emphasizes bad design of
	certain types, such as all of those in Section \ref{badsmells} marked by their
	visual signatures. Even so, our participants found the discovery of bad smell
	to be the most interesting aspect about it, to the point where they could
	imagine business scenarios in which micromanagers use it to ensure precise
	design parameters across a department's spreadsheets! To design in that
	direction, however, would mean a reevaluation of this design goal, since
	intentionally guiding users toward known smells may guide them away from new,
	unmarked ones.

@@

	However, the benefits described in the previous sections imply a hidden
	complication: if the tool educates through example but does not explicitly
	distinguish between good design and bad design, how can we be sure that people
	will not inadvertently learn bad design from it? In the user study, we discussed
	its use in education and smell detection by bringing up the issues surrounding
	the LOOKUP functions; this discussion, though, presupposes a distinguishing eye
	that knew which examples practiced good design and which exhibited the common
	errors. But a beginner might not know the difference. Robillard and Deline, in
	their study, remarked that good API examples should demonstrate best practices,
	but, right now, we have no way to assure this with \toolname. As with the
	problems in achieving unbiased exploration, correcting for this danger may
	entail a reevaluation of design goals.

@@

	\begin{figure} \centering \includegraphics[width=.5\textwidth]{index}
		 \caption{A difficult question: how often is MATCH used in
			both the second and third arguments?} \label{fig:index} \end{figure}

	Though our focus was specifically on function combination, there are several
	other elements of a formula's context that we do no currently consider. For
	example, \toolname does not current capture argument combination; in Figure
	\ref{fig:index}, it is impossible to state how often the function MATCH
	occurred in both the second and third arguments or whether they were more often
	paired with references. Furthermore, it is easy to open a tree and see what is
	used inside of a specific function, but finding information on what a function
	is used inside of takes considerably more work -- we see again in Figure
	\ref{fig:index} that MATCH is used inside INDEX, but we cannot know which
	functions have INDEX inside them without searching every other tree. More
	distant concerns might be exploring which functions often occur in adjacent
	cells in the sheet -- whenever INDEX occurs, which functions are seen most
	often in the cells around it?

@@

	\section{Conclusion} This paper presents a tool to support the exploration of
	function combinations throughout a given spreadsheet dataset. By taking an
	agnostic approach to design quality, it attempts to convey the dataset's
	spreadsheet practices as is: the common along with the anomalous, and the
	well-designed along with the odorous. As seen in the user and case studies,
	this allows it to take on several potential roles at once, such as an
	environment for search out bad code smells as well as a repository for examples
	for learning new techniques. \par
